---
title: "Supporting Information"
author: Martin Sköld^[Corresponding author; mskold@math.su.se, Department of Mathematics, Stockholm university, Stockholm, Sweden] and Jonas Knape^[Department of Ecology, Swedish University of Agricultural Sciences, Uppsala, Sweden]
output:
  pdf_document: default
  html_document: default
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
csl: mee.csl
bibliography: MS_Bounded_rmax.bib
---
```{r, echo = FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(knitr))
table.pars <- function(mcmc.file, species, pars = c("b0", "b1", "b2", "s", "sigma"), 
                       labels = c("Model", "$\\beta_0$", "$\\beta_1$", "$\\beta_2$", "$s$", "$\\sigma$")){
    load(mcmc.file)
    tab_entry <- function(x){
        x <- x[1,,1]
        paste(signif(mean(x), 2), " (", signif(sd(x), 2), ")", sep = "")
    }
    exp_pars <- lapply(out_exp[pars], tab_entry) %>% 
        as.data.frame() %>% 
        bind_cols(data.frame(model = "exponential"), .)
    log_pars <- lapply(out_log[pars], tab_entry) %>% 
        as.data.frame()%>% 
        bind_cols(data.frame(model = "logistic"), .)
kable(rbind(exp_pars, log_pars),
      col.names = labels,
      caption = paste(species, "parameter posterior means and standard deviations."),
      escape = FALSE)
}
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE, eval = TRUE)
```

# Computational details and priors

In order to improve mixing of the MCMC algorithm, we used a reparametrized model updating $\tilde{\beta}=(\tilde{\beta}_0, \tilde{\beta}_1, \tilde{\beta}_2)=(\beta_0+\beta_1\bar{y}, \beta_1, \beta_2)$, where $\bar{y}$ is the mean observed log-count for the species under study. All parameters are given vague priors; $\tilde{\beta}=(\tilde{\beta}_0, \tilde{\beta}_1, \tilde{\beta}_2)$ are apriori independent $N(0,10^6)$ and scale parameters $\sigma$ and $s$ are assumed apriori uniformly distributed on $(0,1000)$.

Samples from the posterior distributions was simulated using JAGS 4.2.0 called from R [@r_development_core_team_r:_2016] using rjags [@plummer_rjags:_2016]. Figures were based on $10^{10}$ iterations subsampled at every 1000 values and with a burn-in period of $10^9$. All code is available at https://github.com/mskoldSU/ReproductiveRates 

# Posterior distributions for all species

Here we provide parameter posterior densities and posterior region abundance for the waterbuck (*Kobus ellipsiprymnus*), giraffe (*Giraffa camelopardalis*), Burchell’s zebra (*Equus burchelli*), greater kudu (*Tragelaphus strepsiceros*), blue wildebeest (*Connochaetes taurinus*), impala (*Aepyceros melampus*) and sable antelope (*Hippotragus niger*).

```{r, echo = FALSE}
table.pars("mcmc/Waterbuck.Rdata", "Waterbuck")
table.pars("mcmc/Giraffe.Rdata", "Giraffe")
table.pars("mcmc/Zebra.Rdata", "Burchell's zebra")
table.pars("mcmc/Blue Wildebeest.Rdata", "Blue wildebeest")
table.pars("mcmc/Impala.Rdata", "Impala")
table.pars("mcmc/Sable.Rdata", "Sable")
```



![_Waterbuck posterior densities for parameters and deviance._](Figs_supp/waterbuck_par_fig.pdf)


![_Posterior median waterbuck abundance together with 50 and 90% credible intervals._](Figs_supp/waterbuck_pop_fig.pdf)



![_Giraffe posterior densities for parameters and deviance._](Figs_supp/giraffe_par_fig.pdf)


![_Posterior median giraffe abundance together with 50 and 90% credible intervals._](Figs_supp/giraffe_pop_fig.pdf)


![_Burchell's zebra posterior densities for parameters and deviance._](Figs_supp/zebra_par_fig.pdf)


![_Posterior median  Burchell's zebra abundance together with 50 and 90% credible intervals._](Figs_supp/zebra_pop_fig.pdf)


![_Greater kudu posterior densities for parameters and deviance._](Figs_supp/kudu_par_fig.pdf)


![_Posterior median greater kudu abundance together with 50 and 90% credible intervals._](Figs_supp/kudu_pop_fig.pdf)


![_Blue wildebeest posterior densities for parameters and deviance._](Figs_supp/wildebeest_par_fig.pdf)


![_Posterior median blue wildebeest abundance together with 50 and 90% credible intervals._](Figs_supp/wildebeest_pop_fig.pdf)


![_Impala posterior densities for parameters and deviance._](Figs_supp/impala_par_fig.pdf)


![_Posterior median impala abundance together with 50 and 90% credible intervals._](Figs_supp/impala_pop_fig.pdf)


![_Sable antelope posterior densities for parameters and deviance._](Figs_supp/sable_par_fig.pdf)


![_Posterior median sable antelope abundance together with 50 and 90% credible intervals._](Figs_supp/sable_pop_fig.pdf)

# References

<div id="refs"></div>
